---
title: "Example_report_rmarkdown"
author: "Adeshina Odugbemi"
output: github_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This document

The aim of this document is to analyze inflammation data from the r-novice-inflammation dataset.

You can find the original data here: <http://swcarpentry.github.io/r-novice-inflammation/setup.html>

### Method

A function to create plots for individual files was created:

```{r}

analyze <- function(filename) {
  
  # takes a filename with relative path
  # reads the csv
  # calculates avg, max, min
  # creates panel of 3 plots
  
  dat <- read.csv(file = filename, header = FALSE)
  
  
  # calculate avg, max, min by column (per day)
  
  avg_day_inflammation <- apply(dat, 2, mean)
  
  max_day_inflammation <- apply(dat, 2, max)
  
  min_day_inflammation <- apply(dat, 2, min)
  
  
  # plot avg, max, min daily inflammation
  
  par(mfrow = c(1, 3)) # set up 1x3 plot panel
  
  plot(avg_day_inflammation, main = filename)
  
  plot(max_day_inflammation, main = filename)
  
  plot(min_day_inflammation, main = filename)
  
  par(mfrow = c(1, 1)) # return plot setting to 1x1
  
}

```

### Data files

```{r}

fnames <- list.files('data', pattern = 'inflammation', full.names = TRUE)

print(fnames)

```




### Example plot

Analyze a single file: `r fnames[1]`

```{r, example-plot}
  
analyze(fnames[1])

```

### All plots

```{r, plot-results}

# create 'results' folder if it doesn't already exist

if (!dir.exists('results')) dir.create('results')


num_plots = 0 # start count of files plotted

for (f in fnames) {
  
  
  # change file format (from .csv to .png)
  
  plot_name <- sub('csv', 'png', f)
  
  
  # change folder (from 'data' to 'results') 
  
  plot_name <- sub('data', 'results', plot_name)
  
  
  # save plots to folder
  
  png(filename = plot_name, width = 900, height = 300)
  
  analyze(f)
  
  dev.off() # remember to close print device!
  
  
  num_plots = num_plots + 1  # added to count of files plotted
  
}

```

Successfully saved `r num_plots` plots to results folder – ignored in git (run Rmd file locally to recreate files).

